Applying Deep Learning to Acoustic Analysis in the PICO-60 Dark Matter Detector

### 2018-07-31 documentation/paper.tex
Defined fiducial cut

>>>>

\subsubsection{Fiducial Cut}

The fiducial cut $FidWallCut(D)$ defines an spatial area along the walls of the vessel within which no events are accepted. It makes use of the bubble position $\chi$, the distance from the bubble to the center of the vessel $R$, and the distance from the bubble to the nearest wall, which is defined as $min(\texttt{Dwall}, \texttt{Dwall\_horiz})$. It is defined as follows:

\begin{itemize}
    \item $Z \leq 523$
    \item Any of the following 4 restrictions are true:
    \begin{itemize}
        \item $(min(\texttt{Dwall}, \texttt{Dwall\_horiz}) > 6) \land (0 < Z \leq 400)$
        \item $(min(\texttt{Dwall}, \texttt{Dwall\_horiz}) > 6) \land (Z \leq 0) \land (R \leq 100)$
        \item $(min(\texttt{Dwall}, \texttt{Dwall\_horiz}) > 13) \land (Z \leq 0) \land (R > 100)$
        \item $(min(\texttt{Dwall}, \texttt{Dwall\_horiz}) > 13) \land (Z > 400)$
    \end{itemize}
\end{itemize}
